

```{r}
library("circular")
library("stats")
library("GGally")
library("dplyr")
library("readxl")
library("sas7bdat")
library("corrplot")
library("tidyverse")
library("car")
library("survival")
library("ggplot2")
library("gridExtra")
library("psych")
library("corrplot")
library("olsrr")
library("cowplot")
library("ggplot2")
library("lmtest")
library("mice")
library("AER")
library("janitor")

```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


*Data cleaning*
```{r}
library(readxl)
Fulldata <- read_xlsx("Fulldata_620W24_Project2.xlsx")
head(Fulldata)
```
```{r}
library(stringr)
time_to_minutes <- function(time_str) {
  if (is.na(time_str) || time_str == "") {
    return(NA)
  }
  matches <- str_match(time_str, "(\\d+h)?(\\d+m)?")
  if (is.na(matches[1,1])) {
    return(NA)
  }

  hours <- ifelse(is.na(matches[1,2]), 0, as.numeric(sub("h", "", matches[1,2])))
  minutes <- ifelse(is.na(matches[1,3]), 0, as.numeric(sub("m", "", matches[1,3])))
  total_minutes <- hours * 60 + minutes
  return(total_minutes)
}

Fulldata$Total.ST.min[!is.na(Fulldata$Total.ST)] <- sapply(Fulldata$Total.ST[!is.na(Fulldata$Total.ST)], time_to_minutes)

Fulldata$Social.ST.min[!is.na(Fulldata$Social.ST)] <- sapply(Fulldata$Social.ST[!is.na(Fulldata$Social.ST)], time_to_minutes)

```

```{r}
library(mice)
mi.Fulldata <- mice(Fulldata, method = "mean")
completed_Fulldata <- complete(mi.Fulldata)
date_numeric_vector <- completed_Fulldata$Date
date_numeric_vector <- as.numeric(date_numeric_vector)
date_as_date_vector <- as.Date(date_numeric_vector, origin = "1899-12-30")
completed_Fulldata$Date <- date_as_date_vector

```
```{r}
completed_Fulldata$Total.ST <- NULL
completed_Fulldata$Social.ST <- NULL

```
```{r}
completed_Fulldata$Proportion.ST <- completed_Fulldata$Social.ST.min/completed_Fulldata$Total.ST.min
completed_Fulldata$Duration.per.use <- completed_Fulldata$Total.ST.min/completed_Fulldata$Pickups

```
```{r}
variable_with_missing <- "Pickup.1st"
if (any(is.na(completed_Fulldata[[variable_with_missing]]))) {
  
  obs_data <- completed_Fulldata[!is.na(completed_Fulldata[[variable_with_missing]]), variable_with_missing]
  mis_data <- completed_Fulldata[is.na(completed_Fulldata[[variable_with_missing]]), variable_with_missing]
  
  imputed_values <- approx(x = seq_along(obs_data), y = obs_data, xout = seq_along(mis_data))$y
  completed_Fulldata[is.na(completed_Fulldata[[variable_with_missing]]), variable_with_missing] <- imputed_values
}


```
```{r}
library(dplyr)
start_date <- as.Date("2024-03-27")
end_date <- as.Date("2024-04-02")

completed_Fulldata <- completed_Fulldata %>%
  mutate(compliance = if_else(Date >= start_date & Date <= end_date, compliance, NA))


Completed_Fulldata=completed_Fulldata
```
```{r}
library(readxl)
df <- read_excel("Fulldata_Baseline.xlsx")
head(df)
```


```{r}
df$pets <- as.numeric(replace(df$pets, df$pets == "No", 0))
```

```{r}
df$sex <- ifelse(df$sex == "male", 1, ifelse(df$sex == "Female", 0, df$sex))

df$sex <- as.numeric(df$sex)

```

```{r}
dfA = df[df$Treatment=="A",]
dfB = df[df$Treatment=="B",]
```


```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


for (column in names(dfA)) {
  if (any(is.na(dfA[[column]]))) {
    # Calculate mode for the column excluding NA values
    mode_value <- getmode(dfA[[column]][!is.na(dfA[[column]])])
    # Replace NA values with the mode
    dfA[[column]][is.na(dfA[[column]])] <- mode_value
  }
}
```


```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

for (column in names(dfB)) {
  if (any(is.na(dfB[[column]]))) {
    # Calculate mode for the column excluding NA values
    mode_value <- getmode(dfB[[column]][!is.na(dfB[[column]])])
    # Replace NA values with the mode
    dfB[[column]][is.na(dfB[[column]])] <- mode_value
  }
}
```

```{r}
basline= rbind(dfA,dfB)
basline$BMI <- NULL
basline
baseline=basline
```


```{r}
#data processing
names(completed_Fulldata)[names(completed_Fulldata) == "pseudo_ID"] <- "pseudo_id"
completed_Fulldata <- completed_Fulldata[!completed_Fulldata$pseudo_id %in% c(9680, 2520, 6759, 8622), ]
basline <- basline[!basline$pseudo_id %in% c(9680, 2520, 6759, 8622), ]

data_4weeks <- completed_Fulldata %>%
  group_by(pseudo_id) %>%
  slice((n() - 27):n()) %>%
  ungroup()

data_4weeks$treat <- ifelse(is.na(data_4weeks$compliance), 0, 1)

na_rows <- completed_Fulldata[is.na(data_4weeks$compliance), ]
average_values <- na_rows %>%
  group_by(pseudo_id) %>% 
  summarise(avg_value = mean(Total.ST.min, na.rm = TRUE))

#normalize average SST
average_values$avg_value <- (average_values$avg_value - mean(average_values$avg_value, na.rm = TRUE)) / 
                               sd(average_values$avg_value, na.rm = TRUE)

data_4weeks <- merge(data_4weeks, basline, by="pseudo_id")

df_combined <- data_4weeks %>%
  left_join(average_values, by = "pseudo_id")

df_combined <- as_tibble(df_combined)

#final 7 days dataframe
finaldata <- df_combined %>%
  group_by(pseudo_id) %>%
  slice_tail(n = 7) %>%
  ungroup()

```


```{r}
names(finaldata)[names(finaldata) == "X2: academic talk"] <- "academic_talk"
names(finaldata)[names(finaldata) == "cousre credit"] <- "cousre_credit"
names(finaldata)[names(finaldata) == "country degree"] <- "country_degree"
names(finaldata)[names(finaldata) == "procrastination score"] <- "procrastination_score"
names(finaldata)[names(finaldata) == "non-academic"] <- "non_academic"

names(data_4weeks)[names(data_4weeks) == "X2: academic talk"] <- "academic_talk"
names(data_4weeks)[names(data_4weeks) == "cousre credit"] <- "cousre_credit"
names(data_4weeks)[names(data_4weeks) == "country degree"] <- "country_degree"
names(data_4weeks)[names(data_4weeks) == "procrastination score"] <- "procrastination_score"
names(data_4weeks)[names(data_4weeks) == "non-academic"] <- "non_academic"

#aggregate last 7 days for each individual
grouped_data <- finaldata %>%
  group_by(pseudo_id) %>%
  summarise(
    total_success = sum(compliance, na.rm = TRUE),
    total_trials = n(),
    workmate = first(workmate),
    academic_talk = first(academic_talk),
    non_academic = first(non_academic),
    pets = first(pets),
    sex = first(sex),
    age = first(age),
    cousre_credit = first(cousre_credit),
    country_degree = first(country_degree),
    job = first(job),
    siblings = first(siblings),
    apps = first(apps),
    devices = first(devices),
    procrastination_score = first(procrastination_score), 
    avg_value = first(avg_value),
    .groups = 'drop'
  )

#interge change
grouped_data$total_success <- as.integer(grouped_data$total_success)
data_4weeks$Pickups <- as.integer(data_4weeks$Pickups)

#plus 1 for zeros since log(0) is infinite
data_4weeks$Total.ST.min[data_4weeks$Total.ST.min == 0] <- data_4weeks$Total.ST.min[data_4weeks$Total.ST.min == 0] + 1

#add weekday_weekend column
data_4weeks$Date <- as.Date(data_4weeks$Date)
data_4weeks$Weekday_Weekend <- ifelse(weekdays(data_4weeks$Date) %in% c('Saturday', 'Sunday'), 1, 0)


#first model
compliance_model <- glm(cbind(total_success, total_trials - total_success) ~ sex + workmate + cousre_credit + apps + procrastination_score + avg_value, family = binomial(), data = grouped_data)
summary(compliance_model)


#second model test

effect_model_test <- glm(data=data_4weeks, Pickups ~ treat + sex + workmate + cousre_credit + apps + procrastination_score + Weekday_Weekend, offset=log(Total.ST.min), family='poisson'(link='log'))
summary(effect_model_test)

residuals_poi <- residuals(effect_model_test)
acf(residuals_poi)

#second model
effect_model <- glm(data=data_4weeks, Pickups ~ lag(Pickups, 1) + lag(Pickups, 2) + treat + sex + workmate + cousre_credit + apps + procrastination_score + Weekday_Weekend, offset=log(Total.ST.min), family='poisson'(link='log'))
summary(effect_model)
```

```{r}
#model diagnostic
#for model 2 (poisson, pickups)
#residual v.s. fitted value
library(ggplot2)
ggplot(effect_model, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red") + 
  labs(x = "Fitted Values", y = "Residuals")
```

```{r}
#overdispersion test
pearson_resid <- residuals(effect_model, type = "pearson")
dispersion_statistic <- sum(pearson_resid^2) / effect_model$df.residual
dispersion_statistic

overdisp_test <- dispersiontest(effect_model, trafo = 1)
print(overdisp_test)

#quasi test
quasi_model <- glm(Pickups ~ treat + sex + workmate + cousre_credit + apps + procrastination_score, offset=log(Total.ST.min), family = quasipoisson(link = "log"), data = data_4weeks)
summary(quasi_model)

#AIC score
AIC(effect_model)

#Q-Q plot
plot(effect_model,2)

# Check for influential points
ols_plot_resid_lev(effect_model)


```

```{r}
#for model 1 (binomial, compliance)
#Residual plot (residual v.s. fitted value)
library(ggplot2)
ggplot(compliance_model, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red") + 
  labs(x = "Fitted Values", y = "Residuals")

#AIC score
AIC(compliance_model)

#Q-Q plot
plot(compliance_model,2)

# Check for influential points
ols_plot_resid_lev(compliance_model)

#check for multicollinearity
vif(compliance_model)

#check for goodness of fit
if(!require(ResourceSelection)){install.packages("ResourceSelection")}
library(ResourceSelection)
hoslem.test(compliance_model$y, fitted(compliance_model), g = 10)


```

$$
visualization
$$
```{r}
library("circular")
library("stats")
library("GGally")
library("dplyr")
library("readxl")
library("sas7bdat")
library("corrplot")
library("tidyverse")
library("car")
library("survival")
library("ggplot2")
library("gridExtra")
library("psych")
library("corrplot")
library("olsrr")
library("cowplot")
library("ggplot2")
library("lmtest")
```

```{r}
not= c(9680, 2520, 6759, 8622)
Completed_Fulldata$pseudo_id=Completed_Fulldata$pseudo_ID
Completed_Fulldata <-Completed_Fulldata[Completed_Fulldata$Date >= as.Date("2024-03-06") & Completed_Fulldata$Date <= as.Date("2024-04-02"), ]
data_all <- merge(Completed_Fulldata, baseline, by="pseudo_id")
data_all <- data_all[data_all$Date >= as.Date("2024-03-06") & data_all$Date <= as.Date("2024-04-02"), ]

data_all <- subset(data_all, !(pseudo_ID %in% c(9680, 2520, 6759, 8622)))

```


```{r}
convert_fraction_to_time <- function(time_fraction) {
  if (is.na(time_fraction)) {
    return(NA)  
  }
  hours <- time_fraction * 24
  hour_part <- floor(hours)
  minute_part <- round((hours - hour_part) * 60)
   return(sprintf("%02d:%02d", hour_part, minute_part))
}


Completed_Fulldata$Pickup.1st <- as.numeric(Completed_Fulldata$Pickup.1st)
Completed_Fulldata$Pickup.1st <- sapply(Completed_Fulldata$Pickup.1st, convert_fraction_to_time)

head(Completed_Fulldata)



```
```{r}
data_all <- merge(Completed_Fulldata, baseline, by="pseudo_id")

data_all <- subset(data_all, !(pseudo_ID %in% c(9680, 2520, 6759, 8622)))

```

angle change
```{r}
convert_time_to_fraction <- function(time_str) {

  time <- as.POSIXct(time_str, format = "%H:%M", tz = "UTC")
  seconds_from_midnight <- as.numeric(difftime(time, trunc(time, "days"), units = "secs"))
  # 
  seconds_from_midnight / (24 * 60 * 60)
}

# 
data_all$angle <- sapply(data_all$Pickup.1st, convert_time_to_fraction)

# 


```
angle change
```{r}
convert_time_to_fraction <- function(time_str) {

  time <- as.POSIXct(time_str, format = "%H:%M", tz = "UTC")
  seconds_from_midnight <- as.numeric(difftime(time, trunc(time, "days"), units = "secs"))
  # 
  seconds_from_midnight / (24 * 60 * 60)
}

# 
data_all$angle <- sapply(data_all$Pickup.1st, convert_time_to_fraction)

# 



```


```{r}
library(dplyr)

# 
times <- strptime(data_all$Pickup.1st, format = "%H:%M")

# 
hours <- as.numeric(format(times, "%H"))
minutes <- as.numeric(format(times, "%M"))

time_in_hours <- hours + minutes / 60 

# 
Pickup.1st_angle <- (time_in_hours / 24) * 360

# 
data_all <- cbind(data_all, Pickup.1st_angle)
data_all
```
hist base line workmate
```{r}
library(ggplot2)
library(dplyr)
dfA = df[df$Treatment=="A",]
dfB = df[df$Treatment=="B",]
baseline$treatment=baseline$Treatment
baseline_a = subset(baseline, treatment == "A")
baseline_b = subset(baseline, treatment == "B")
baseline <- clean_names(baseline)
baseline_a <- clean_names(baseline_a)
baseline_b <- clean_names(baseline_b)

baseline$dataset <- 'Treatment'
baseline_a$dataset <- 'Treatment A'
baseline_b$dataset <- 'Treatment B'


combined_data <- rbind(baseline, baseline_a, baseline_b)

combined_data$dataset <- factor(combined_data$dataset, levels = c("Baseline", "Baseline A", "Baseline B"))

# Create a facetted histogram
ggplot(combined_data, aes(x = workmate)) +
  geom_histogram(bins = 30) + 
  facet_wrap(~ dataset, scales = "free_y") +
  theme_minimal() +
  xlab("Workmate") +
  ylab("Frequency")

```

$$
group ALL
$$
```{r}
describe(baseline)
sum(baseline$sex==1)/34 # percentage of male
sum(baseline$country_degree==1)/34 #Country where previous degree received (US=1, Non-US=0)
sum(baseline$job==1)/34#Currently have a job (>10 hours/week) such as RA/TA/Others (Yes =1, No=0)

```
code for screen time
```{r}

data_all_baseline <- data_all[data_all$Date >= as.Date("2024-03-06") & data_all$Date <= as.Date("2024-03-26"), ]
data_all_treatment <- data_all[data_all$Date >= as.Date("2024-03-27") & data_all$Date <= as.Date("2024-04-02"), ]

data_all_baseline_a = subset(data_all_baseline, Treatment == "A")
data_all_baseline_b = subset(data_all_baseline, Treatment == "B")
data_all_treatment_a = subset(data_all_treatment, Treatment == "A")
data_all_treatment_b = subset(data_all_treatment, Treatment == "B")

data_all_baseline$Individual <- 'base_all'
data_all_baseline_a$Individual <- 'base_a'
data_all_baseline_b$Individual <- 'base_b'

data_all_treatment$Individual <- 'treat_all'
data_all_treatment_a$Individual <- 'treat_a'
data_all_treatment_b$Individual <- 'treat_b'
```

 first pickup
```{r}
first.pickup.cir_data_all_baseline = circular(data_all_baseline$Pickup.1st_angle, units = "degrees", template = "clock24")
plot(first.pickup.cir_data_all_baseline, stack = TRUE, bins = 48, col = "blue")

first.pickup.cir_data_all_treatment = circular(data_all_treatment$Pickup.1st_angle, units = "degrees", template = "clock24")
plot(first.pickup.cir_data_all_treatment, stack = TRUE, bins = 48, col = "blue")


```
Occupation time curves

```{r}
variables2 <- list(
  Total.ST.min = "Total.ST.min",
  Proportion.ST = "Proportion.ST",
  Duration.per.use = "Duration.per.use"
)
calculate_cum_prob <- function(df, variable_name) {
  variable_data <- na.omit(df[[variable_name]])
  unique_values <- sort(unique(variable_data), decreasing = F) 
  freq <- table(factor(variable_data, levels = unique_values))
  cum_freq <- rev(cumsum(rev(freq))) 
  cum_prob <- cum_freq / sum(freq)
  return(data.frame(Value = names(cum_prob),  magnitude = unique_values, CumulativeProbability = cum_prob))
}

```

curve for all
```{r}
OTC_plots_data_all_baseline <- list()
for (var_name in names(variables2)) {
  df_cum_prob <- calculate_cum_prob(data_all_baseline, var_name)

  p <- ggplot(df_cum_prob, aes(x = magnitude, y = CumulativeProbability)) +
    geom_point() + 
    labs(title = paste(variables2[[var_name]], "base"), x = "magnitude", y = "P(x >= c)") +
    theme_minimal()
  OTC_plots_data_all_baseline[[var_name]] <- p
}
do.call(grid.arrange, c(OTC_plots_data_all_baseline, ncol = 3))

```
```{r}
OTC_plots_data_all_treatment <- list()
for (var_name in names(variables2)) {
  df_cum_prob <- calculate_cum_prob(data_all_treatment, var_name)

  p <- ggplot(df_cum_prob, aes(x = magnitude, y = CumulativeProbability)) +
    geom_point() + 
    labs(title = paste(variables2[[var_name]], "treat"), x = "magnitude", y = "P(x >= c)") +
    theme_minimal()
  OTC_plots_data_all_treatment[[var_name]] <- p
}
do.call(grid.arrange, c(OTC_plots_data_all_treatment, ncol = 3))

```
ACF plots for continues covariates

```{r}
variables <- c('Total.ST.min', 'Proportion.ST', 'Duration.per.use')
acf_results <- list()
```
grp all
```{r}
par(mfrow=c(1, 3))
for (var in variables) {
  acf_result <- acf(data_all_baseline[[var]], plot = TRUE, main = paste("ACF for", var))
  acf_results[[var]] <- acf_result
}
for (var in variables) {
  print(paste("ACF values for", var, ":"))
  print(acf_results[[var]]$acf)
}
par(mfrow=c(1, 1))
#------------------------------------
par(mfrow=c(1, 3))
for (var in variables) {
  acf_result <- acf(data_all_treatment[[var]], plot = TRUE, main = paste("ACF for", var))
  acf_results[[var]] <- acf_result
}
for (var in variables) {
  print(paste("ACF values for", var, ":"))
  print(acf_results[[var]]$acf)
}
par(mfrow=c(1, 1))

```
time serise
```{r}
data_combined_baseline <- rbind( data_all_baseline_a, data_all_baseline_b)
data_combined_treatment <- rbind( data_all_treatment_a, data_all_treatment_b)
```
baseline TST
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Total.ST.min
TST_data_all_baseline <- ggplot(data_all_baseline, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time for ALL baseline", x = "Date", y = "Screen Time (mins)")
TST_data_all_baseline_a <- ggplot(data_all_baseline_a, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time for Interventation A for baseline", x = "Date", y = "Screen Time (mins)")
TST_data_all_baseline_b <- ggplot(data_all_baseline_b, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time for Interventation B for baseline", x = "Date", y = "Screen Time (mins)")
grid.arrange(TST_data_all_baseline, TST_data_all_baseline_a, TST_data_all_baseline_b, nrow = 3)

ggplot(data_combined_baseline, aes(x = Date, y = Total.ST.min, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time",
       x = "Date",
       y = "Screen Time (mins)") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```
treatment TST
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Total.ST.min
TST_data_all_treatment <- ggplot(data_all_treatment, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time for ALL treatment", x = "Date", y = "Screen Time (mins)")
TST_data_all_treatment_a <- ggplot(data_all_treatment_a, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time for Interventation A for treatment", x = "Date", y = "Screen Time (mins)")
TST_data_all_treatment_b <- ggplot(data_all_treatment_b, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time for Interventation B for treatment", x = "Date", y = "Screen Time (mins)")
grid.arrange(TST_data_all_treatment, TST_data_all_treatment_a, TST_data_all_treatment_b, nrow = 3)

ggplot(data_combined_treatment, aes(x = Date, y = Total.ST.min, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Total Screen Time",
       x = "Date",
       y = "Screen Time (mins)") +
  theme_minimal() +
  scale_color_manual(values = c("treat_all" = "blue"))


```
baseline Pickups
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Pickups
Pickups_data_all_baseline <- ggplot(data_all_baseline, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups for ALL baseline", x = "Date", y = "Pickups")
Pickups_data_all_baseline_a <- ggplot(data_all_baseline_a, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups for Interventation A for baseline", x = "Date", y = "Pickups")
Pickups_data_all_baseline_b <- ggplot(data_all_baseline_b, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups for Interventation B for baseline", x = "Date", y = "Pickups")
grid.arrange(Pickups_data_all_baseline, Pickups_data_all_baseline_a, Pickups_data_all_baseline_b, nrow = 3)

ggplot(data_combined_baseline, aes(x = Date, y = Pickups, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of Dailypickups",
       x = "Date",
       y = "Pickups") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```
treatment Pickups
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Pickups
Pickups_data_all_treatment <- ggplot(data_all_treatment, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups Time for ALL treatment", x = "Date", y = "Pickups")
Pickups_data_all_treatment_a <- ggplot(data_all_treatment_a, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups Time for Interventation A for treatment", x = "Date", y = "Pickups")
Pickups_data_all_treatment_b <- ggplot(data_all_treatment_b, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups Time for Interventation B for treatment", x = "Date", y = "Pickups")
grid.arrange(Pickups_data_all_treatment, Pickups_data_all_treatment_a, Pickups_data_all_treatment_b, nrow = 3)

ggplot(data_combined_treatment, aes(x = Date, y = Pickups, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups Time",
       x = "Date",
       y = "Pickups") +
  theme_minimal() +
  scale_color_manual(values = c("treat_all" = "blue"))
```
baseline Proportion_of_SST
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Pickups
Proportion.ST_data_all_baseline <- ggplot(data_all_baseline, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST for ALL baseline", x = "Date", y = "Proportion.ST")
Proportion.ST_data_all_baseline_a <- ggplot(data_all_baseline_a, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST for Interventation A for baseline", x = "Date", y = "Proportion.ST")
Proportion.ST_data_all_baseline_b <- ggplot(data_all_baseline_b, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST for Interventation B for baseline", x = "Date", y = "Proportion.ST")
grid.arrange(Proportion.ST_data_all_baseline, Proportion.ST_data_all_baseline_a, Proportion.ST_data_all_baseline_b, nrow = 3)

ggplot(data_combined_baseline, aes(x = Date, y = Proportion.ST, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST",
       x = "Date",
       y = "Proportion.ST") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```
treatment proportion.
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Proportion.ST
Proportion.ST_data_all_treatment <- ggplot(data_all_treatment, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST Time for ALL treatment", x = "Date", y = "Proportion.ST")
Proportion.ST_data_all_treatment_a <- ggplot(data_all_treatment_a, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST Time for Interventation A for treatment", x = "Date", y = "Proportion.ST")
Proportion.ST_data_all_treatment_b <- ggplot(data_all_treatment_b, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST Time for Interventation B for treatment", x = "Date", y = "Proportion.ST")
grid.arrange(Proportion.ST_data_all_treatment, Proportion.ST_data_all_treatment_a, Proportion.ST_data_all_treatment_b, nrow = 3)

ggplot(data_combined_treatment, aes(x = Date, y = Proportion.ST, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Proportion.ST Time",
       x = "Date",
       y = "Proportion.ST") +
  theme_minimal() +
  scale_color_manual(values = c("treat_all" = "blue"))
```
baseline Duration per use
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Duration.per.use
Duration.per.use_data_all_baseline <- ggplot(data_all_baseline, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Duration.per.use for ALL baseline", x = "Date", y = "Duration.per.use")
Duration.per.use_data_all_baseline_a <- ggplot(data_all_baseline_a, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Duration.per.use for Interventation A for baseline", x = "Date", y = "Duration.per.use")
Duration.per.use_data_all_baseline_b <- ggplot(data_all_baseline_b, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Duration.per.use for Interventation B for baseline", x = "Date", y = "Duration.per.use")
grid.arrange(Duration.per.use_data_all_baseline, Duration.per.use_data_all_baseline_a, Duration.per.use_data_all_baseline_b, nrow = 3)

ggplot(data_combined_baseline, aes(x = Date, y = Duration.per.use, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of DailyDuration.per.use",
       x = "Date",
       y = "Duration.per.use") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```
treatment duration
```{r}
#Time Series plots
Sys.setlocale("LC_TIME", "en_US")

#Duration.per.use
Duration.per.use_data_all_treatment <- ggplot(data_all_treatment, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Duration.per.use Time for ALL treatment", x = "Date", y = "Duration.per.use")
Duration.per.use_data_all_treatment_a <- ggplot(data_all_treatment_a, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Duration.per.use Time for Interventation A for treatment", x = "Date", y = "Duration.per.use")
Duration.per.use_data_all_treatment_b <- ggplot(data_all_treatment_b, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Duration.per.use Time for Interventation B for treatment", x = "Date", y = "Duration.per.use")
grid.arrange(Duration.per.use_data_all_treatment, Duration.per.use_data_all_treatment_a, Duration.per.use_data_all_treatment_b, nrow = 3)

ggplot(data_combined_treatment, aes(x = Date, y = Duration.per.use, color = Individual)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Duration.per.use Time",
       x = "Date",
       y = "Duration.per.use") +
  theme_minimal() +
  scale_color_manual(values = c("treat_all" = "blue"))
```
TST
```{r}
library(dplyr)

data_all_baseline$Date <- as.Date(data_all_baseline$Date)

average_values_per_day_baseline <- data_all_baseline %>%
  group_by(Date) %>%
  summarise(
    Total.ST.min = median(Total.ST.min, na.rm = TRUE),
    Pickups = median(Pickups, na.rm = TRUE),
    Duration.per.use = median(Duration.per.use, na.rm = TRUE),
    Proportion.ST = median(Proportion.ST, na.rm = TRUE)
  )

print(average_values_per_day_baseline)

ggplot(average_values_per_day_baseline, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Total.ST.min",
       x = "Date",
       y = "Total.ST.min") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```


```{r}
library(dplyr)

data_all_treatment$Date <- as.Date(data_all_treatment$Date)

average_values_per_day_treatment <- data_all_treatment %>%
  group_by(Date) %>%
  summarise(
    Total.ST.min = median(Total.ST.min, na.rm = TRUE),
    Pickups = median(Pickups, na.rm = TRUE),
    Duration.per.use = median(Duration.per.use, na.rm = TRUE),
    Proportion.ST = median(Proportion.ST, na.rm = TRUE)
  )

ggplot(average_values_per_day_treatment, aes(x = Date, y = Total.ST.min)) +
  geom_line() +
  labs(title = "Time Series Plot of Total.ST.min",
       x = "Date",
       y = "Total.ST.min") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```

pickup
```{r}
ggplot(average_values_per_day_baseline, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily pickups",
       x = "Date",
       y = "DailyPickups") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
```

```{r}
ggplot(average_values_per_day_treatment, aes(x = Date, y = Pickups)) +
  geom_line() +
  labs(title = "Time Series Plot of Daily Pickups",
       x = "Date",
       y = "DailyPickups") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```
duration 
```{r}
ggplot(average_values_per_day_baseline, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Duration.per.use",
       x = "Date",
       y = "Duration.per.use") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
```

```{r}
ggplot(average_values_per_day_treatment, aes(x = Date, y = Duration.per.use)) +
  geom_line() +
  labs(title = "Time Series Plot of Duration.per.use",
       x = "Date",
       y = "Duration.per.use") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```
proportion
```{r}
ggplot(average_values_per_day_baseline, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Proportion.ST",
       x = "Date",
       y = "Proportion.ST") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
```

```{r}
ggplot(average_values_per_day_treatment, aes(x = Date, y = Proportion.ST)) +
  geom_line() +
  labs(title = "Time Series Plot of Proportion.ST",
       x = "Date",
       y = "Proportion.ST") +
  theme_minimal() +
  scale_color_manual(values = c("base_all" = "blue"))
#ggsave("timeseries_plot.png", plot = p, width = 10, height = 6, units = "in")
```
each success avg credit
```{r}
library(ggplot2)


ggplot(grouped_data, aes(x = factor(total_success), y = cousre_credit, fill = factor(total_success))) +
  geom_bar(stat = "summary", fun = "mean") + 
  labs(x = "Total Success", y = "Average Course Credit", fill = "Total Success") +
  theme_minimal() +
  coord_flip() +  
  ggtitle("Average Course Credit by Total Success")


```
